\vspace{-1cm}\normalsize{\textbf{Fairly Random: Impact of Winning the Toss on the Probability of Winning}}

### 2015-12-13 write_up/cricket.tex
a couple more to go

\begin{figure}[htbp]
\centering
\caption{Percentage of Matches Won Minus Matches Lost After Winning the Toss by Type of Match}
\includegraphics[scale=.85]{../figs/winbyType.pdf}
\label{fig:type}
\end{figure}

@@

\begin{figure}[htbp]
\centering
\caption{Percentage of Matches Won Minus Matches Lost After Winning the Toss By Day/Night}
\includegraphics[scale=.85]{../figs/winbyDayNight.pdf}
\label{fig:dn}
\end{figure}

@@

\begin{figure}[htbp]
\centering
\caption{Percentage of Matches Won Minus Matches Lost After Winning the Toss by Duckworth-Lewis}
\includegraphics[scale=.85]{../figs/winbyDL.pdf}
\label{fig:dl}
\end{figure}

>>>>

\begin{figure}[htbp]
\centering
\caption{Difference in Winning Percentages of Teams that Won the Toss and Teams that Lost the Toss by Type of Match}
\includegraphics[scale=.85]{../figs/winbyType.pdf}
\label{fig:type}
\end{figure}

@@

\begin{figure}[htbp]
\centering
\caption{Difference in Winning Percentages of Teams that Won the Toss and Teams that Lost the Toss by Day or Day and Night}
\includegraphics[scale=.85]{../figs/winbyDayNight.pdf}
\label{fig:dn}
\end{figure}

@@

\begin{figure}[htbp]
\centering
\caption{Difference in Winning Percentages of Teams that Won the Toss and Teams that Lost the Toss by Whether or not Duckworth-Lewis was invoked}
\includegraphics[scale=.85]{../figs/winbyDL.pdf}
\label{fig:dl}
\end{figure}
